RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-26 paper/paper7/paper7.tex
set focus on constraint type classification

\newenvironment{DL}{
  %\scriptsize
  %\sffamily
  \vspace{0cm}
  \begin{tabular}{r l}

}{
  \end{tabular}
  %\linebreak
}

@@

In this paper, we propose a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements.
Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary\tb{vocabulary-independent}. 
Within the context of a complex and complete real world running example within the community around research data for the \emph{social, behavioural, and economic (SBE) sciences}, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
We show how data in rectangular format and metadata on record-unit data sets (i.e., data about individuals, households, businesses) or more specifically person-level data sets, aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.\tb{record-unit or more specific person-level data sets}
We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality and trust.
We exhaustively evaluated the metadata quality of large real world aggregated, person-level, and thesauri data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types.
\tb{DCAT und XKOS nur im future work}
\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Rectangular Data, SKOS, XKOS, Linked Data, Semantic Web}
\end{abstract}

@@

%The remainder of the paper is structured as follows.
For the extensive evaluation, we implemented 53 constraint types by instantiating 212 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets (section \ref{implementation}).
First, several \emph{SBE} domain experts evaluated the correctness (i.e., the gold standard) of all constraints and therefore the generic applicability of the developed constraint classification system. 
Second, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types (section \ref{evaluation}).

@@

\section{RDF Constraints Classification}
\label{classification}

Bosch et al. identified 74 requirements to formulate RDF constraints (e.g. \emph{R-75, R-81: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each expressed by different constraint languages.
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.

We developed a system to classify RDF constraints and RDF constraint types.
Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
%\emph{data model specific constraint types} (e.g. \emph{data model consistency})
The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses two disjoint \textbf{\emph{sets of constraint types}}:
\begin{enumerate}
	\item $\mathcal{CT}_{C}$: \emph{Content-Driven Constraint Types}\tb{complex constraints / zahlen interpretierbar / in einem bestimten vokabulare werden viele basic constraints verletzt / daten haben bessere qualität vokabular / wichtigkeit constraint languages, dass complexe constraints beschrieben}
	\item $\mathcal{CT}_{T}$: \emph{Technology-Driven Constraint Types}\tb{basic constraints / welche constraints können automatisch abgeleitet werden / bestimmte constraints werden in den vokabularen definiert bzw sehr leicht zu implementieren wäre / studie ohne daten macht keinen sinn --> cardinality restriction / alle constraints die mit rdf + rdfs + owl definiert werden können / vokabukare werden heutzutage mit rdf / rdfs / owl beschrieben / constraints die typischerweise hinterlegt werden / constraints die amn als vokabular}
\end{enumerate}

\tb{große datenbestände untersuchen um ein besseres verständnis zu bekommen / liste von constraints / jedes einzelne constraint für jeded einzelne vokabular severity level / warum severity was bringt das}

$\mathcal{CT}_{C}$ (\emph{Content-Driven Constraint Types}) is the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models (section \ref{content-driven-validation}). 
Therefore, domain experts may formulate $\mathcal{CT}_{C}$ constraints manually in prose English which is technically expressed by a constraint language afterwards.
For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques (constraint type: \emph{structure}). 
A thesaurus, e.g., should not contain many orphan concepts (concepts without any associative or hierarchical relations) lacking valuable context information for search and retrieval.  
$\mathcal{CT}_{T}$ (\emph{Technology-Driven Constraint Types}) is the set of constraints which can be generated completely automatically out of vocabularies' data models (section \ref{technology-driven-validation}).
With \emph{minimum qualified cardinality restrictions} (\emph{R-74}), e.g., one can restrict that
a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column} (in DL: \ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column})\footnote{For simplicity reasons, we do not use namespace prefixes in DL statements.}.

\emph{SBE} experts \tb{todo / wieviele constraints welche klasse} determined the default \textbf{\emph{severity level}} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \textbf{\emph{sets of constraints}}:
\begin{itemize}
	\item $\mathcal{SL}_{0}$: set of constraints with severity level \emph{informational}
	\item $\mathcal{SL}_{1}$: set of constraints with severity level \emph{warning}
	\item $\mathcal{SL}_{2}$: set of constraints with severity level \emph{error}
\end{itemize}
Violations of $\mathcal{SL}_{0}$ constraints point to possible data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically or semantically not correctly represented.
The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that $\mathcal{SL}_{1}$ invalid data could be
whereas $\mathcal{SL}_{1}$ invalid data cannot be processed further. 
Although, we provide default severity levels for each constraint, users should be able to specify constraints' severity levels according to their individual needs, i.e., use case specific severity levels.

We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 212 constraints (classified as 53 constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
In this section, we describe constraints, which are important to ensure \emph{SBE} (meta)data quality, 
associate them with default severity levels, and assign them to $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraint types.

@@

\subsection{Technology-Driven Constraint Types}
\label{technology-driven-validation}

$\mathcal{CT}_{T}$ constraints can be directly and automatically derived from explicitly stated syntax and semantics of vocabularies' data models.
Thus, associated default severity levels are in most cases very strong ($\mathcal{SL}_{2}$).

%\textbf{Constraints Derived From Vocabularies.}
\textbf{Vocabulary.}
One should not invent new or use deprecated terms (e.g. \emph{disco:containsVariable}) of vocabularies (\emph{vocabulary}).
\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships (\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}) and
\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
The constraint types \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names.
\emph{R-223} serves to make sure that all literal values are valid with regard to their datatypes.
Thus, all date values (e.g. {\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}) must be of the datatype \emph{xsd:date} and \emph{xsd:nonNegativeInteger} values (e.g. \emph{disco:frequency}) do not have to be negative.

\textbf{Existential Quantifications.}
\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
Case quantity measures how many cases are collected for a study.
High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
Variables should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school},.e.g, is associated with the theoretical concept \emph{Child Care}. 
The constraint's severity level is weak, as in most cases research can be continued without having information about theoretical concepts.

\textbf{Cardinality Restrictions on Properties and Language Tags.}
%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
A \emph{phdd:TableStructure}, e.g., has (\emph{phdd:column}) at least one \emph{phdd:Column} (\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}),
a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
%DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
%02: Unique data set (IC-1 [3]) - Every qb:Observation has (qb:dataSet) ex-
%actly one associated qb:DataSet (Observation  ¥1 dataSet.DataSet [
%¤1 dataSet.DataSet).
%Severity level: ERROR
%
%(\emph{R-75: minimum qualified cardinality restrictions})
%
%DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-
%02: Unique DSD (IC-2 [3]) - Every qb:DataSet has (qb:structure) exactly one
%associated qb:DataStructureDefinition (DataSet  ¥1 structure.DataStructureDefinition
%[ ¤1 structure.DataStructureDefinition).
%Severity level: ERROR
%
%(\emph{R-74: exact qualified cardinality restrictions})
%\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
%\textbf{Language Tag Cardinality.}
For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48, R-49}):
(1) Some controlled vocabularies contain literals in natural language, but without information what language has actually been used. 
(2) Language tags must conform to language standards. 
(3) Some thesaurus concepts are labeled in only one, others in multiple languages. It may be desirable to have each concept labeled in each of the languages that are also used on the other concepts. Although not always possible, incompleteness of language coverage for some concepts may indicate shortcomings of thesauri
\cite{MaderHaslhoferIsaac2012}.

\textbf{Disjointness and Allowed Values.}
All properties, not having the same domain and range types, are defined to be pairwise disjoint
(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
All \emph{XKOS} classes are pairwise disjoint (\emph{R-7: disjoint classes}; e.g. \ms{ClassificationLevel $\sqcap$ ConceptAssociation $\sqsubseteq$ $\perp$}),
i.e., individuals cannot be instances of multiple disjoint classes.
It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g. 'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g. \emph{xsd:string}). 
\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}).

\textbf{Validation and Reasoning.}
Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
With \emph{subsumption} (\emph{R-100}), one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} must also be part of the \emph{skos:Collection} class extension (\ms{ClassificationLevel $\sqsubseteq$ Collection}).
With \emph{sub properties} (\emph{R-54, R-64}), one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study (\ms{fundedBy $\sqsubseteq$ contributor}).
%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}. 
%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
Per default, however, access to data sets should be restricted (\emph{false}).
Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
If \emph{dcterms:coverage} and one of its sub-properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are present,
it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties. 
This validation can indicate when the data is verbose (redundant) or expressed at a too general level and could thus be improved.

\subsection{Content-Driven Constraint Types}
\label{content-driven-validation}

>>>>

\newenvironment{DL}{
  %\scriptsize
  %\sffamily
  \vspace{0cm}
	\begin{center}
  \begin{tabular}{c l}

}{
  \end{tabular}
	\end{center}
}

@@

In this paper, we propose a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements.
Constraints are instantiated from constraint types in order to validate both metadata and data independently from used vocabularies. 
Within the context of a complex and complete real world running example within the community around research data for the \emph{social, behavioural, and economic (SBE) sciences}, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
We show how data in rectangular format and metadata on person-level or more generally record-unit data sets (i.e., data about individuals, households, businesses), aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.
We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality and trust.
We exhaustively evaluated the metadata quality of large real world aggregated, person-level, and thesauri data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types.
\tb{DCAT und XKOS nur in future work}
\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Rectangular Data, SKOS, XKOS, Linked Data, Semantic Web}
\end{abstract}

@@

%The remainder of the paper is structured as follows.
For the extensive evaluation, we implemented 53 constraint types by instantiating 213 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets (section \ref{implementation}).
First, several \emph{SBE} domain experts evaluated the correctness (i.e., the gold standard) of all constraints and therefore the generic applicability of the developed constraint classification system. 
Second, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types (section \ref{evaluation}).

@@

\section{Classification of Constraint Types and Constraints}
\label{classification}

Bosch et al. identified 76 requirements to formulate RDF constraints (e.g. \emph{R-75, R-81: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each expressed by different constraint languages.
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.

We developed a system to classify RDF constraints and RDF constraint types.
Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
%\emph{data model specific constraint types} (e.g. \emph{data model consistency})

We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints (classified as 53 distinct constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
In this section, we describe constraints, which are important to ensure \emph{SBE} (meta)data quality, 
associate them with default severity levels, and assign them to $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraint types.

\subsection{Classification of Constraint Types}

The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses three disjoint \emph{sets of constraint types}:
\begin{enumerate}
	\item \textbf{$\mathcal{CT}_{B}$: \emph{Basic Constraint Types}}
	\item \textbf{$\mathcal{CT}_{S}$: \emph{Simple Constraint Types}}
	\item \textbf{$\mathcal{CT}_{C}$: \emph{Complex Constraint Types}}
\end{enumerate}

The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to define vocabularies.
\emph{Basic constraint types} ($\mathcal{CT}_{B}$) 
denotes the set of constraint types whose constraints 
can be extracted completely automatically out of vocabularies.
As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
\emph{basic constraints} ensure that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
%The {\em existential quantification} (\emph{R-86}) 
%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (\emph{DL}), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
\emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
This way, it is expressible in OWL 2 that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
\begin{ex}
[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
    owl:minQualifiedCardinality 1 ;
    owl:onProperty column ;
    owl:onClass Column ] .
\end{ex}

\emph{Simple constraint types} ($\mathcal{CT}_{S}$) is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
The {\emph{data property facets} (\emph{R-46}) $\mathcal{CT}_{S}$ constraint type enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).

\emph{Complex constraint types} ($\mathcal{CT}_{C}$) encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
Complex constraints show the importance of constraint languages enabling to describe complex constraints.
For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
An example of such \emph{structure} constraints is that 
a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.

\tb{refer to evaluation / what do we want to know?}

\subsection{Classification of Constraints}

\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \emph{sets of constraints}:
\begin{itemize}
	\item $\mathcal{SL}_{0}$: set of constraints with \textbf{severity level \emph{informational}}
	\item $\mathcal{SL}_{1}$: set of constraints with \textbf{severity level \emph{warning}}
	\item $\mathcal{SL}_{2}$: set of constraints with \textbf{severity level \emph{error}}
\end{itemize}
Violations of $\mathcal{SL}_{0}$ constraints point to desirable data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically and/or semantically not correctly represented.
The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that data, not conforming to $\mathcal{SL}_{1}$ but conforming to $\mathcal{SL}_{2}$ constraints, could be processed further,
whereas data, not corresponding to $\mathcal{SL}_{2}$ constraints, cannot be processed further after validation. 
Although, we provide default severity levels for each constraint, validation environments should enable users to adapt constraints' severity levels according to their individual needs.

As $\mathcal{CT}_{B}$ constraints are derived from explicitly stated semantics of vocabularies' data models, 
default severity levels of $\mathcal{CT}_{B}$ constraints are in most cases very strong ($\mathcal{SL}_{2}$) and 
in average stronger than severity levels of $\mathcal{CT}_{S}$ and $\mathcal{CT}_{C}$ constraints.
As a consequence, violating many $\mathcal{CT}_{B}$ constraints is an indicator for bad data quality\footnote{For simplicity reasons, we only assign severity levels to $\mathcal{CT}_{B}$ constraints when they differ from $\mathcal{SL}_{2}$.}.

@@

\section{Basic Constraint Types}
\label{basic-constraint-types}

As \emph{RDFS} and \emph{OWL} are typically used to define vocabularies, \emph{RDFS} and \emph{OWL} reasoning may be performed prior to validation. 
Reasoning and validation are indeed very closely related. 
\emph{Reasoning} is the process of determining what follows from what has been stated.
%Both should be possible: (1) validation with reasoning and (2) validation without reasoning. 
We divide the whole set of \emph{basic constraint types} ($\mathcal{CT}_{B}$) into two disjoint sets to investigate the affect of reasoning to the validation process: 
\begin{enumerate}
	\item $\mathcal{C}_B ^{\mathcal{R}}$ corresponds to axioms in \emph{OWL 2} and denotes the set of constraint types which enable performing reasoning prior to validation, especially when not all the knowledge is explicit (section \ref{basic-constraint-types-with-reasoning}).  
  \item $\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense (section \ref{basic-constraint-types-without-reasoning}).
\end{enumerate}

\subsection{Basic Constraint Types with Reasoning}
\label{basic-constraint-types-with-reasoning}

Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
Reasoning as an optional pre validation step is beneficial for RDF validation as 
(1) it may resolve constraint violations and  
(2) it may cause useful constraint violations.
A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
%\begin{DL}
%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
%\end{DL}
Consider the following DL knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly. For simplicity reasons, we only write namespace prefixes in DL statements to avoid ambiguities.}:

\begin{center}
\begin{DL} 
$\mathcal{K}=\{$ &\ms{LogicalDataSet $\sqsubseteq$ dcat:DataSet},\\
 &\ms{LogicalDataSet $\sqsubseteq \forall$ aggregation.qb:DataSet},\\
 %&\ms{dcat:DataSet $\equiv$ $\exists$ dcat:distribution . dcat:Distribution},\\
 &\ms{LogicalDataSet( logical-data-set )},\\
 &\ms{aggregation( logical-data-set, aggregated-data-set )}
 \}\\ 
\end{DL}
\end{center}

As we know that only person-level data sets (\emph{disco:LogicalDataSet}) can derive (\emph{disco:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
{\em logical-data-set} is a \emph{disco:LogicalDataSet}, 
and \emph{aggregated-data-set} is derived from \emph{logical-data-set},
we conclude that \emph{aggregated-data-set} must be a \emph{qb:DataSet}.
As \emph{aggregated-data-set} is not explicitly defined to be a \emph{qb:DataSet}, however, a constraint violation is raised.
If we perform reasoning prior to validation, the constraint violation is resolved, as the implicit triple \ms{qb:DataSet(aggregated-data-set)} is inferred.

Reasoning may also cause constraint violations which are needed to enhance data quality.
With \emph{subsumption} (\emph{R-100}), one can state that \emph{disco:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
i.e., each person-level data set is also a catalog data set.
Thus, constraints on catalog data sets are also validated for person-level data sets;
e.g., the \emph{existential quantification} below restricting that person-level data sets must have a distribution:

\begin{center}
\begin{DL} 
$\mathcal{K}=\{$ 
 &\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
&\ms{Variable $\equiv$ $\exists$ concept.Concept}
 \}\\ 
\end{DL}
\end{center}

We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
%Case quantity measures how many cases are collected for a study.
%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).

\begin{center}
\begin{DL} 
$\mathcal{K}=\{$ 
  &\ms{fundedBy $\sqsubseteq$ contributor}
 \}\\ 
\end{DL}
\end{center}

By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.

%\begin{DL}
%fundedBy $\sqsubseteq$ contributor
%\end{DL}

%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}. 
%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).

%\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
%Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
%\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
%\begin{DL}
%$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
%$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
%\end{DL}

%\begin{center}
%\begin{DL} 
%$\mathcal{K}=\{$ 
  %&\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}, \\
	%&\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}, \\
	%&\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition} \\ 
	%&\ms{$\sqcap$ $\leq$1 structure.DataStructureDefinition}
 %\}\\ 
%\end{DL}
%\end{center}
